Development of a educational and sustainable robotic platform for children and adults

### 2013-10-23 doc/paper.tex
autocommited by makefile

\begin{description}
\item[\stars{5}] The evaluated aspect fully complies with the assessment critera and adds additional functionality which exceeds expectations. 
\item[\stars{4}] The evaluated aspect fully complies with the assessment critera. Mentioned properties may have minor restraints which do not affect the overall rating of the system.
\item[\stars{3}]foo
\item[\stars{2}]foo
\item[\stars{1}]foo
\item[\stars{0}] The evaluated aspect does not comply with 
\end{description}

>>>>

\begin{description}
\item[\stars{5}] \hfill \\The evaluated aspect fully complies with the assessment critera and adds additional functionality which exceeds expectations. 
\item[\stars{4}] \hfill \\The evaluated aspect fully complies with the assessment critera. Mentioned properties may have minor restraints which do not affect the overall quality/functionality of the system.
\item[\stars{3}] \hfill \\The evaluated aspect complies with most of the assessment critera. The evaluation shows that some minor and/or major restraints exist which may affect the overall quality/functionality.
\item[\stars{2}] \hfill \\The evaluated aspect mets the assessment critera partially but shows severe restraints affecting the overall quality/functionality.
\item[\stars{1}] \hfill \\The evaluated aspect contains the rudiments of the assessment critera.
\item[\stars{0}] \hfill \\The evaluated aspect does not met the assessment critera in any way. 
\end{description}
